---
title: "MGT 6203 Project -- Team070"
output: 
  html_notebook: 
    fig_width: 14
---

import libraries
```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
'installations'
install.packages('tidyquant')
install.packages('dplyr')
install.packages('ggplot2')
install.packages('ggpubr')
install.packages('directlabels')


library(tidyquant)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(directlabels)

```

This segment of the code will import the Google Mobility Data for USA between 15 Feb 2020 to 26 Mar 2022
```{r echo=TRUE}
get_mob_data <- function(){
  mob_data <- read.csv("US_Mobility_Data.csv")
  mob_data <- mob_data %>% mutate(date = as.Date(date, format = '%d/%m/%Y'))
  mob_data <- mob_data[,c('date','retail_and_recreation_percent_change_from_baseline')]
  names(mob_data)[names(mob_data) == 'retail_and_recreation_percent_change_from_baseline']<-'retail_and_recreation_mobility'
  
  return (mob_data)
}

mob_data <- get_mob_data()

mob_data_plot <- ggplot(data = mob_data, aes(x = date, y = retail_and_recreation_mobility))
mob_data_plot + geom_point(color = 'blue') + labs(x = 'date', y = 'Retail and Recreation Mobility Percent change from baseline')

```

Importing financial data using TidyQuant

```{r echo=TRUE}

get_price <- function(ticker,start_date, end_date){
  price <- c(ticker) %>% tq_get(get='stock.prices', from=start_date,to=end_date)
  return (price)
}

start_date <- '2020-01-03'
end_date <- '2022-03-26'

XRT <- get_price('XRT', start_date, end_date)
DIS <- get_price('DIS', start_date, end_date)
SEAS <- get_price('SEAS', start_date, end_date)
DBI <- get_price('DBI', start_date, end_date)
M <- get_price('M',start_date, end_date)

```
creating function for data preparation

```{r}
get_percent_change <- function(asset){
  asset_sub <- asset[(asset$date >= '2020-01-03' &  asset$date<= '2020-02-06'),]
  baseline <- median(asset_sub$adjusted)
  asset$percent_from_baseline <- (asset$adjusted/baseline - 1) *100
  return (asset[,c('date','percent_from_baseline')])
}

XRT_processed <- get_percent_change(XRT)
DIS_processed <- get_percent_change(DIS)
SEAS_processed <- get_percent_change(SEAS)
DBI_processed <- get_percent_change(DBI)
M_processed <- get_percent_change(M)

merged <-  merge(mob_data,XRT_processed, by = 'date')
names(merged)[names(merged) == 'percent_from_baseline']<-'XRT_percent_from_baseline'
merged <-  merge(merged,DIS_processed, by = 'date')
names(merged)[names(merged) == 'percent_from_baseline']<-'DIS_percent_from_baseline'
merged <-  merge(merged,SEAS_processed, by = 'date')
names(merged)[names(merged) == 'percent_from_baseline']<-'SEAS_percent_from_baseline'
merged <-  merge(merged,DBI_processed, by = 'date')
names(merged)[names(merged) == 'percent_from_baseline']<-'DBI_percent_from_baseline'
merged <-  merge(merged,M_processed, by = 'date')
names(merged)[names(merged) == 'percent_from_baseline']<-'M_percent_from_baseline'

all_data <- merged
summary(all_data)
```
Plotting graph
```{r}
ggplot()+ 
  geom_point(data = all_data, aes(x = date, y=retail_and_recreation_mobility, color = 'retail_and_recreation_mobility')) + 
  geom_line(data = all_data, aes(x = date, y=XRT_percent_from_baseline, color = 'XRT_percent_from_baseline'))  + 
  geom_line(data = all_data, aes(x = date, y=DIS_percent_from_baseline, color = 'DIS_percent_from_baseline'))  + 
  geom_line(data = all_data, aes(x = date, y=SEAS_percent_from_baseline, color = 'SEAS_percent_from_baseline'))  + 
  geom_line(data = all_data, aes(x = date, y=DBI_percent_from_baseline, color = 'DBI_percent_from_baseline'))  + 
  geom_line(data = all_data, aes(x = date, y=M_percent_from_baseline, color = 'M_percent_from_baseline'))  + 
  scale_color_manual(name = "Legend", values = c("retail_and_recreation_mobility" = "red", "XRT_percent_from_baseline" = "blue", 'DIS_percent_from_baseline' = "green", 'SEAS_percent_from_baseline' = 'black','DBI_percent_from_baseline' = 'purple','M_percent_from_baseline' = 'cyan' ))+
  labs(x = 'Date', y = 'Percantage from baseline') +
  ggtitle("Plot of percentage change from baseline of google mobility data and asset prices ")

```


data visualisation
```{r}

merge_data <- function(mob_data, asset_data){
  merged <- merge(mob_data, asset_data, by = 'date')
  data <- merged[,c('date','percent_from_baseline','retail_and_recreation_mobility')]
  return (data)
}

plot_price_mob <- function(mob_data, asset_data){
  data <- merge_data(mob_data,asset_data)
  plot <- ggplot(data, aes(date, y = value)) + geom_line(aes(y=percent_from_baseline, color = 'blue')) + geom_point(aes(y=retail_and_recreation_mobility, color = 'red'))
  
  return (plot)
}

'plotting graphs'
XRT_plot <- plot_price_mob(mob_data, XRT_processed)+ggtitle('XRT and Google Mob plot') + labs(x = 'Date', y = '% from baseline') + theme(legend.position = 'none')
DIS_plot <- plot_price_mob(mob_data, DIS_processed)+ggtitle('DIS and Google Mob plot') + labs(x = 'Date', y = '% from baseline') + theme(legend.position = 'none')
SEAS_plot <- plot_price_mob(mob_data, SEAS_processed)+ggtitle('SEAS and Google Mob plot') + labs(x = 'Date', y = '% from baseline') + theme(legend.position = 'none')
DBI_plot <- plot_price_mob(mob_data, DBI_processed)+ggtitle('DBI and Google Mob plot') + labs(x = 'Date', y = '% from baseline') + theme(legend.position = 'none')
M_plot <- plot_price_mob(mob_data, M_processed)+ggtitle('M and Google Mob plot') + labs(x = 'Date', y = '% from baseline') + theme(legend.position = 'none')
ggarrange(XRT_plot, DIS_plot, SEAS_plot, DBI_plot, M_plot, ncol = 2, nrow = 3)

```

Training linear regression model

```{r echo=TRUE}

linear_reg <- function(mob_data, asset_data){
  data <- merge_data(mob_data,asset_data)
  model <- lm(percent_from_baseline ~ retail_and_recreation_mobility, data = data)
  print(summary(model))
  res <- resid(model)
  plot(data$retail_and_recreation_mobility, res, ylab = 'Residuals', xlab = 'Google Mobility')
  return (model)
}


log_linear_reg <- function(mob_data, asset_data){
  data <- merge_data(mob_data,asset_data)
  data$log_price_percent_from_baseline <- log(data$percent_from_baseline + 100)
  model <- lm(log_price_percent_from_baseline ~ retail_and_recreation_mobility, data = data)
  print(summary(model))
  res <- resid(model)
  plot(data$retail_and_recreation_mobility, res, ylab = 'Residuals', xlab = 'Google Mobility')
  
  return (model)
}

linear_log_reg <- function(mob_data, asset_data){
  data <- merge_data(mob_data,asset_data)
  data$log_retail_and_recreation_mobility <- log(data$retail_and_recreation_mobility + 100)
  model <- lm(percent_from_baseline ~ log_retail_and_recreation_mobility, data = data)
  print(summary(model))
  res <- resid(model)
  plot(data$retail_and_recreation_mobility, res, ylab = 'Residuals', xlab = 'Google Mobility')
  
  return (model)
}

log_log_reg <- function(mob_data, asset_data){
  data <- merge_data(mob_data,asset_data)
  data$log_retail_and_recreation_mobility <- log(data$retail_and_recreation_mobility + 100)
  data$log_price_percent_from_baseline <- log(data$percent_from_baseline + 100)
  model <- lm(log_price_percent_from_baseline ~ log_retail_and_recreation_mobility, data = data)
  print(summary(model))
  res <- resid(model)
  plot(data$retail_and_recreation_mobility, res, ylab = 'Residuals', xlab = 'Google Mobility')
  
  return (model)
}


XRT_linear_reg <- linear_reg(mob_data,XRT_processed)
XRT_log_linear_reg <- log_linear_reg(mob_data,XRT_processed)
XRT_linear_log_reg <- linear_log_reg(mob_data,XRT_processed)
XRT_log_log_reg <- log_log_reg(mob_data,XRT_processed)


# linear regression models for partial data of each assets
# percent from baseline -> asset data; retail_and_recreation -> mobility data
data <- merge_data(mob_data,SEAS_processed)
sub_data <- data[(data$date>= '2020-02-08' &  data$date<= '2020-07-08'),]
head(sub_data)
# visualization of overall assets vs mobility in partial time frame
ggplot(sub_data, aes(date, y = value)) + geom_line(aes(y=percent_from_baseline), color = 'blue') + geom_point(aes(y=retail_and_recreation_mobility), color = 'red')
SEAS_sub_linear<-lm(percent_from_baseline ~ retail_and_recreation_mobility, data = sub_data)
summary(SEAS_sub_linear) #significant

data <- merge_data(mob_data,DIS_processed)
sub_data <- data[(data$date>= '2020-02-08' &  data$date<= '2020-07-08'),]
head(sub_data)
DIS_sub_linear<-lm(percent_from_baseline ~ retail_and_recreation_mobility, data = sub_data)
summary(DIS_sub_linear) #significant

data <- merge_data(mob_data,XRT_processed)
sub_data <- data[(data$date>= '2020-02-08' &  data$date<= '2020-07-08'),]
head(sub_data)
XRT_sub_linear<-lm(percent_from_baseline ~ retail_and_recreation_mobility, data = sub_data)
summary(XRT_sub_linear) #significant

data <- merge_data(mob_data,DBI_processed)
sub_data <- data[(data$date>= '2020-02-08' &  data$date<= '2020-07-08'),]
head(sub_data)
DBI_sub_linear<-lm(percent_from_baseline ~ retail_and_recreation_mobility, data = sub_data)
summary(DBI_sub_linear) #significant

data <- merge_data(mob_data,M_processed)
sub_data <- data[(data$date>= '2020-02-08' &  data$date<= '2020-07-08'),]
head(sub_data)
M_sub_linear<-lm(percent_from_baseline ~ retail_and_recreation_mobility, data = sub_data)
summary(M_sub_linear) #significant



```
Linear-Linear Regression model of XRT against google mobility data

```{r}
XRT_linear_reg <- linear_reg(mob_data,XRT_processed)
```

Log-Linear Regression model of XRT against google mobility data

```{r}
XRT_log_linear_reg <- log_linear_reg(mob_data,XRT_processed)
```

Linear-Log Regression model of XRT against google mobility data
```{r}
XRT_linear_log_reg <- linear_log_reg(mob_data,XRT_processed)
```
Log-Log Regression model of XRT against google mobility data
```{r}
XRT_log_log_reg <- log_log_reg(mob_data,XRT_processed)
```

```{r}

```































